Introduction: a pipeline to analyse time-course gene expression data

### 2019-05-01 scripts/00_introduction.Rmd
Expanding introduction

The authors find that

**XXX Add summary of the key findings of the the paper**

>>>>

By combining gene expression time-course data with virus growth data, the
authors show that the inflammatory response of lung tissue is gated until a
threshold of the virus concentration is  exceeded in the lung. Once this
threshold is exceeded, a strong inflammatory and cytokin production occurs.
This results provides evidence that the pathology response is non-linearly
regulated by virus concentration.
